\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-17 experience.tex
update to address some comments by Akash

Towards testing the MigratingTable library, the developers wrote an in-memory reference implementation of the \texttt{IChainTable} interface, called \texttt{SpecTable}, which can be used for comparing the output of MigratingTable on an arbitrary input history. This enabled sampling from a distribution, which was defined over all possible input histories within certain bounds. \psharp takes control of the choice of input history, so that it can systematically explore different input scenarios.

>>>>

Towards testing the MigratingTable library, the developers wrote an in-memory reference implementation of the \texttt{IChainTable} interface, called \texttt{SpecTable}, which can be used for comparing the output of MigratingTable on an arbitrary input history. This enabled sampling from a distribution that was defined over all possible input histories within certain bounds. The \psharp systematic testing engine automatically takes care of enumerating different input histories.

### 2015-09-17 methodology.tex
update to address some comments by Akash

All internal timers of ExtMgr are disabled, because it is crucial to delegate all non-determinism to \psharp. Instead, the EN expiration loop and the extent repair loop are driven by external timers provided by \psharp. Note that system correctness should {\em not} hinge on the frequency of any individual timer. Hence, \psharp has the complete freedom to schedule arbitrary interleavings between the timers.

>>>>

All internal timers of ExtMgr are disabled, because it is crucial to delegate all non-determinism to \psharp. Instead, the EN expiration loop and the extent repair loop are driven by external timers modeled in \psharp. Note that system correctness should {\em not} hinge on the frequency of any individual timer. Hence, the \psharp systematic testing engine has the complete freedom to schedule arbitrary interleavings between the timers.
